Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

>>>>

\begin{table}[]
	\caption{Experiment Result for Alpha of 0.1}
	\label{test-1}
	\begin{tabular}{lcc}
		\textbf{ID} & \multicolumn{1}{l}{\textbf{Regression Detected}} & \multicolumn{1}{l}{\textbf{Critical Path Analysis Correct}} \\
		IS1 & Yes & Yes \\
		IS2 & Yes & Yes \\
		IS3 & Yes & Yes \\
		IS4 & Yes & Yes \\
		IS5 & Yes & Yes \\
		IS6 & Yes & Yes \\
		IS7 & Yes & Yes \\
		ES1 & Yes & Yes \\
		ES2 & Yes & Yes \\
		ES3 & Yes & Yes \\
		ES4 & Yes & Yes
	\end{tabular}
\end{table}
